\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-30 OaklandSubmission/pipe.tex
nits in S4

Given $\prog$, partitioning first decomposes $\prog$ into
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$ with the guarantee that the
circuits generated for every $\progn_i$, as defined above, are small
enough to fit in the machine memory. We then compile and execute the
$k$ programs $\progn_1,\progn_2,\ldots,\progn_k$ sequentially
(freeing up memory usage after execution of each $\progn_i$) to
finally output $z$ to both parties.

@@

Our current implementation of secure code partitioning requires a manual step.
In particular, the developer needs to decompose the large program $\prog$ into 
the sequence of small programs $\prog_1\seq\dots\seq\prog_k$ manually.
Then \tool generates sequence of programs $\progn_1,\dots\progn_k$ automatically.
Automating this decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave
the construction of such an analysis as future work.

>>>>

Thus, given a decomposition of $\prog$ into
$\prog_1\seq\prog_2\seq\dots\seq\prog_k$, we can use the construction
above to generate programs $\progn_1,\progn_2,\ldots,\progn_k$, that
can be sequentially executed, using the unmodified underlying \mpc
backend. The following theorem state the correctness and security of
the scheme.

@@

\subsubsection*{Managing circuit sizes using partitioning}
We use partitioning for programs that require large
circuits. Specifically, the programmer decomposes the program
$\prog$ into a sequence of small programs
$\prog_1\seq\dots\seq\prog_k$ manually. And then, \tool generates
sequence of programs $\progn_1,\dots\progn_k$ automatically. We then
compile and execute the $k$ programs
$\progn_1,\progn_2,\ldots,\progn_k$ sequentially, freeing up memory
usage after execution of each $\progn_i$.
Automating the manual decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave
the construction of such an analysis as future work.
